### 2023-06-08 manuscript.Rmd
- added "A comment on..." to title (in line with other comments) - added departments and location to affiliations

---
title             : "Assessing rigor and impact of research software for hiring and promotion in psychology"
#subtitle          : "Commentary: 'Responsible Research Assessment II: A specific proposal for hiring and promotion in psychology'"
shorttitle        : "Assessing research software"

@@

affiliation:
  - id            : "1"
    institution   : "MSB Medical School Berlin"
  - id            : "2"
    institution   : "Max Planck Institute for Human Development"
  - id            : "3"
    institution   : "Max Planck UCL Centre for Computational Psychiatry and Ageing Research"
  - id            : "4"
    institution   : "Humboldt-Universität zu Berlin"

>>>>

---
title             : "Assessing rigor and impact of research software for hiring and promotion in psychology: A comment on Gärtner et al. (2022)"
#subtitle          : "Commentary: 'Responsible Research Assessment II: A specific proposal for hiring and promotion in psychology'"
shorttitle        : "Assessing research software"

@@

affiliation:
  - id            : "1"
    institution   : "Department of Psychology, MSB Medical School Berlin, Berlin, Germany"
  - id            : "2"
    institution   : "Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany"
  - id            : "3"
    institution   : "Max Planck UCL Centre for Computational Psychiatry and Ageing Research, Berlin, Germany"
  - id            : "4"
    institution   : "Department of Psychology, Humboldt-Universität zu Berlin, Berlin, Germany"
